% CHTC Student Handbook

\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
% Change font to Helvetica
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

% TODO - Add glossary
% \usepackage{glossaries}

\usepackage{hyperref}
\usepackage{multirow}

\addtolength{\oddsidemargin}{-.875in}
\addtolength{\evensidemargin}{-.875in}
\addtolength{\textwidth}{1.75in}
\addtolength{\topmargin}{-.875in}
\addtolength{\textheight}{1.75in}

\begin{document}
% TITLE PAGE
\title{CHTC Student Handbook \\
    \large Edition 0.1}
\author{Center for High Throughput Computing}
\date{\today}
\maketitle

% TABLE OF CONTENTS
\tableofcontents
\clearpage

% BEGIN BOOK
\section{Student Work 101}
    \subsection{Tasks and Workflow}
        As a student worker for the CHTC you will be responsible for a large variety
        of tasks to help keep the CHTC Cluster up and running, but there a few basic
        things you will find yourself doing most often. Our primary job is to fix
        individual machines in the cluster that go down. Most often machines can
        be brought down by kernel panics, networking issues, or hardware issues.
        To fix a machine, we take a simple approach to diagnose the issue and come
        up with a solution.

        \begin{enumerate}
            \item Diagnose the problem. You might need to plug into the machine
            with a console, or SSH into it if it is still online. If a machine
            kernel panics it will often print a memory stack trace to the console
            and freeze up. You will need to physically reboot the machine to proceed.
            \item Find a solution. Often times rebooting the machine will clear up
            minor problems such as kernel panics or networking issues.
            \begin{itemize}
                \item Kernel Panic (crash) - reboot, check server for errors.
                \item Networking issue - reboot machine or restart networking, then
                go to advanced networking troubleshooting if still needed.
                \item Hardware issue - diagnose the hardware issue and fix it.
                (Replace a bad disk, make note of a bad RAID card, etc)
            \end{itemize}
            \item Fix the problem and confirm that condor is running jobs again.
            \begin{itemize}
                \item his might mean rebooting the machine, rebuilding the machine,
                replacing a bad disk and rebuilding, or something else entirely.
                Fix it if possible. If not - make note of the issue in the ticket
                and await further instructions.
            \end{itemize}
        \end{enumerate}

        Some other tasks you might be assigned include, but are not limited to:
        archiving condor releases to DVD, building new execute machines, working
        with Dell/Cisco Tech Support to get replacement parts, moving servers, a
        nd other random tasks assigned by full time CHTC staff.
    \subsection{RT Ticket System}
        We use the Request Tracker (RT) Ticket System for managing work at the CHTC.
        \href{https://crt.cs.wisc.edu/rt/}{crt.cs.wisc.edu} is the web address to
        access our Request Tracker.This will be your home for managing work tickets.
        The basic flow is: You are assigned a ticket, click on the ticket name to
        open it. By default, your 10 highest priority, or newest, tickets will be
        listed on your home page. You can view all of your tickets by clicking the
        “10 Highest Priority Tickets I Own” link (counter-intuitive, I know).

        Once you have selected a ticket, you can read all correspondence related
        to that particular issue. Under the “actions” button (top right) the most
        common things you will do are “reply” and “resolve.” Whenever you make
        changes to a machine, make sure to log what you did in the ticket. When
        the machine is fixed or the task is completed, you can resolve the ticket.

    \subsection{Monitoring Nodes}
        You can monitor the cluster on \href{monitor0.chtc.wisc.edu}{monitor0.chtc.wisc.edu}.
        This has links to Icinga, our host monitoring application, Grafana, and Ganglia.
        All of these are extremely powerful tools that can be used to monitor the
        status of machines in the cluster and diagnose problems with individual nodes.

    \subsection{How to Use This Guide}
        \begin{itemize}
            \item Any line or section beginning with “\$” is a command line operation.
            Enter it directly as it appears, without the preceding “\$”.
            \item Any bracketed item (eg. [System Name]) needs to be replaced with
            the corresponding entity. (eg. change [System Name] $\rightarrow$
            e1000.chtc.wisc.edu).
            \item Following the step-by-step walkthroughs to complete most basic
            tasks and use this as a reference manual.
            \item The appendix includes a complete list of node locations, useful
            for location a machine for physical changes (hard reboot, HDD swap, etc).
            \item If you find an error in this guide, or you want to contribute, head on over
            to https://github.com/dcchambers/CHTC-Student-Handbook and file a bug report or
            submit a pull request with your own changes!

        \end{itemize}

\clearpage

\section{Rebuilding a Node}
    Rebuilding nodes is one of the primary responsibilities of student CHTC employees.
    Here’s a step-by-step walkthrough for you.

    \begin{enumerate}
        \item Enable netboot in cobbler.
        \begin{enumerate}
            \item Via Command Line:
            \begin{enumerate}
                \item SSH into wid-service-1.chtc.wisc.edu
                \item {\fontfamily{cmtt}\selectfont \$ sudo cobbler system edit
                --name=[server name] --netboot-enabled=True }
                \item Check that netboot is enabled $\rightarrow$
                {\fontfamily{cmtt}\selectfont \$ sudo cobbler system report
                --name=[server name] }
                \item Sync Cobbler $\rightarrow$ {\fontfamily{cmtt}\selectfont
                \$ sudo cobbler sync }
            \end{enumerate}
            \item Via Web Interface
            \begin{enumerate}
                \item Open \href{https://wid-service-1.chtc.wisc.edu/cobbler_web}{Cobbler}
                in your web browser
                \item Click on “Systems” under the Configuration tab on the left side.
                \item Find the node you want to rebuild and click on it’s name in
                the list to open the node configuration tool.
                \item Alternatively, navigate directly to \\
                wid-service-1.chtc.wisc.edu/cobbler\_web/system/edit/[node name]
                \item Click on the “general” drop down button to reveal more options
                \item Check the “enable netboot” option
                \item Hit “save” on the bottom of the page
                \item When you are redirected to the cobbler system list page,
                hit “Sync” Under the Actions tab on the left side.
                \item Once you get a popup notification on the top-right of the
                screen, the sync has complete. This may take a few seconds.
            \end{enumerate}
            \item Make sure you have the correct profile enabled in Cobbler as
            well. If you are doing a standard rebuild you probably won’t have to
            change it, but make sure if it’s a multi-disk execute node that it is
            set to the correct SL66 Exec profile.
        \end{enumerate}
        \item Reboot the machine and netboot it.
        \begin{enumerate}
            \item Most machines are set to netboot by default, meaning if you
            reboot them they will search for a netboot entry and if they find it,
            they will netboot automatically. If a machine is not netbooting automatically,
            you may need to press a button on the keyboard (Often F12) when it POSTS
            in order to force it to netboot. If you have tried these and it still
            won’t boot from the network, go into the BIOS and change the boot order
            to set netboot as boot priority \#1.
            \item If done correctly, it should launch the Scientific Linux installer.
            Once you see this is happening, move on to the next step.
            \item To diagnose problems with the boot process, when the loading bar appears, you can press Alt+d to display a verbose boot screen.
        \end{enumerate}
        \item Run Puppet.
        \begin{enumerate}
            \item We are going to need to run puppet once the machine is rebuilt
            in order to configure it.
            \item While the machine is rebuilding, SSH into wid-service-1.chtc.wisc.edu
            \item Run this command: {\fontfamily{cmtt}\selectfont \$ sudo puppetca
            -c [node name] } on wid-service-1.
            \item If you do this before the machine finishes rebuilding, it may
            run puppet automatically when it rebuilds. To see if it is doing this:
            When the machine is booting Scientific Linux, hit an arrow key
            $\leftarrow$ or $\rightarrow$, or ALT+D on the console keyboard to view the
            verbose boot log. If the log is paused on “{\fontfamily{cmtt}\selectfont Starting:
            anamon…     [OK] }” for a while, that mean’s it’s running puppet. Good
            job! Once it finishes booting now, you should be able to log in with your username.
            \item If the machine does not run puppet automatically, connect a console
            to the machine and log in as a root user (ask Admin for root login)
            \item ON THE TARGET NODE: run {\fontfamily{cmtt}\selectfont \$ sudo rm -rvf /var/lib/puppet/ssl }
            (After clearing the puppet files from wid-service-1 in the previous
            steps). DO NOT RUN THIS ON wid-service-1.
            \item After clearing the puppet files from wid-service-1 in the previous
            steps, run {\fontfamily{cmtt}\selectfont \$ sudo rm -rvf /var/lib/puppet/ssl }
            on the target node. DO NOT RUN THIS ON wid-service-1.
            \item Then run {\fontfamily{cmtt}\selectfont \$ sudo puppetd -tv
            --configtimeout=1000 }
            \item Note: Puppet will not run if networking is broken (try to restart
            networking or reboot the machine if this is the case) or the system
            clock is broken. To set the clock run: {\fontfamily{cmtt}\selectfont
            \$ rdate -s ntp.doit.wisc.edu }
        \end{enumerate}
        \item Log in and confirm condor is running.
            \begin{enumerate}
                \item Once puppet finishes running, you should be able to log in
                with your own username
                \item Confirm condor is running: {\fontfamily{cmtt}\selectfont \$
                condor\_status \$HOSTNAME }
                \item You should also see Condor running with {\fontfamily{cmtt}\selectfont
                \$ ps aux | grep condor }
            \end{enumerate}
    \end{enumerate}
\clearpage

\section{Building a New Node}
    TODO - Elaborate. \\

    Building a new node is very similar to rebuilding a current machine, with the
    added caveat of configuring the node in Cobbler and DHCP.
    \begin{enumerate}
        \item First, we need to create a new entry for the node in Cobbler. You
        should be provided a hostname and IP address to use for the new machine.
        You can create a new Cobbler entry via the Web interface or CLI.
        \begin{itemize}
            \item Via Web Interface
            \begin{itemize}
                \item Go to cobbler web.
                \item Create a new system. The Easiest way to do this is to copy
                an existing execute node entry and change the relevant information.
                \item Open up the new machine entry you just created and change the
                hostname, IP address, and MAC address. Make sure to do this under the
                correct network interface (generally eth0).
                \item Make sure you selected the correct profile. Generally,
                you will use one of the SL6.6 profiles for execute nodes.
                \item Enable netboot, save it, and sync cobbler once it's configured
                correctly.
            \end{itemize}
            \item Via CLI
            \begin{itemize}
                \item TODO - CLI Intsructions.
            \end{itemize}
        \end{itemize}
        \item Next, we need to create a DHCP entry for this machine.
        \begin{itemize}
            \item DHCP is managed by different machines depending on the node location.
            \begin{itemize}
                \item B240: cobbler-b240
                \item 2360/CSL \& WID Data Center: wid-service-1
                \item 3370: host-6
            \end{itemize}
            \item SSH into the correct server and become root. Then open up /etc/dhcp/dhcpd.conf in VIM.
            \item Copy an existing execute node entry and edit it to create a new entry with the
            correct IP and MAC address of the new machine. Save the file.
            \item run {\fontfamily{cmtt}\selectfont \$ service dhcpd restart } - if
            an error comes up, you screwed up the .conf file.
        \end{itemize}
        \item You should now have the new node set up in Cobbler and DHCP. You can follow
        the standard steps to build a node at this point. Netboot the machine, run puppet,
        and make sure it's running jobs once it's finished.
    \end{enumerate}
\clearpage

\section{Decommissioning a Node}
    \begin{enumerate}
        \item Label the server for spare parts with ticket \#, or SWAP it.
        \begin{itemize}
            \item If you SWAP a server, remove the HDDs and any hardware that might be useful (eg, RAM).
            \item If it has a CSL Inventory Sticker, email the CSL with the Inventory number
            and tell them you are sending the server to SWAP.
            \item Drop the server off in the SWAP area of the CS basement (by the elevators).
        \end{itemize}
        \item Remove it from the DHCP config.
        \begin{itemize}
            \item SSH into the relevant DHCP server.
            \begin{itemize}
                \item B240: cobbler-b240
                \item 2360/CSL \& WID Data Center: wid-service-1
                \item 3370: host-6
            \end{itemize}
            \item Become root with {\fontfamily{cmtt}\selectfont \$ sudo -i }
            \item Open up the dhcpd.conf file under /etc/dhcp/dhcpd.conf on the correct server.
            \item Delete the entry for the server you are decommissioning.
            \item Restart DHCP - Run {\fontfamily{cmtt}\selectfont \$ sudo service dhcpd restart }, make
            sure that it restarts OK. If not, you deleted something you shouldn't have.
        \end{itemize}
        \item Remove it's cobbler system object.
            \begin{itemize}
                \item From the cobbler web interface, view the list of systems by going to \\
                https://wid-service-1.chtc.wisc.edu/cobbler\_web/system/list
                \item Locate the server on the list, and then press the "Delete" button next to it.
                \item Sync cobbler. (Press the "Sync" button under actions.)
            \end{itemize}
        \item Remove it's puppet entry.
            \begin{itemize}
                \item SSH into wid-service-1, and become root.
                \item Open up the correct file in this directory: /etc/puppet/environments/production/modules/site/manifests/chtc/nodes/
                \begin{itemize}
                    \item B240: chtcexecsl66\_b240.pp
                    \item 2360/CSL: chtcexecsl66\_2360.pp
                    \item WID Data Center: chtcexecsl66\_wid.pp
                    \item 3370: chtcexecsl66\_3370a.pp
                \end{itemize}
                \item Delete the puppet entry for the server you are decommissioning.
            \end{itemize}
        \item Remove it's Icinga \& Nagios entry.
            \begin{itemize}
                \item Icinga
                \begin{itemize}
                    \item SSH into monitor0.chtc.wisc.edu
                    \item Become root and open up /etc/icinga2/conf.d/hosts.conf
                    \item Delete the entry for the server you are decommissioning.
                    \item Restart Icinga - Run {\fontfamily{cmtt}\selectfont \$ sudo service icinga2 restart }
                \end{itemize}
                \item Nagios
                \begin{itemize}
                    \item SSH into monitor.chtc.wisc.edu
                    \item Become root and open up /etc/nagios/objects/hosts.cfg
                    \item Delete the entry for the server you are decommissioning.
                    \item Restart Nagios - Run {\fontfamily{cmtt}\selectfont \$ sudo service nagios restart }
                \end{itemize}
            \end{itemize}
        \item Remove it's htcondor configuration host/*.local file (Ask Moate to do this).
    \end{enumerate}


\clearpage

\section{Creating Tickets}
    If you don't have any tickets assigned to you in your RT Queue that you can
    work on, then you can go ahead and create your own tickets for work that needs
    to be done.\\

    We'll use a simple example to outline how to create tickets.\\

    Let's say your queue is empty - you can log into Icinga (Or another monitoring
    tool that we use) to look for any nodes that might be offline or experiencing
    other issues.

    \begin{enumerate}
        \item Head to monitor0.chtc.wisc.edu in your browser.
        \item Click on the link to Icinga, and log in (ask Admin for login info).
        This will take you to the Icinga dashboard. From here, you can get a basic
        overview of server status.
        \item Look for machines listed under the "Host Problems" section.
        \begin{itemize}
            \item Let's say we see a node, e1000.chtc.wisc.edu, listed under that section
            with the status message "Critical - Host Unreachable".
            \item Click on that host to bring up information about it. From here,
            you can get a better overview of what's wrong with the machine. In this case,
            the machine is "Down" - offline for whatever reason. It might have crashed,
            it might be powered off, we don't know yet. All we know is that Icinga can't
            connect to it.
        \end{itemize}
        \item Great, now that we see a server is down, we need to check RT to see if
        a ticket already exists for this issue.
        \begin{itemize}
            \item Log in to RT (crt.cs.wisc.edu) in a new tab.
            \item Start a new search - select "New Search" under the "Tickets" tab
            at the top of the screen.
            \item Enter the server name (e1000) in the "Subject" box, and make sure
            the relational selector is set to "Matches".
            \item Click on "Add these terms and search".
        \end{itemize}
        \item At this point, you will either see (a) ticket(s) matching the server,
        or none at all. We want only want to have 1 ticket for managing each server, so
        it is important to not open new tickets when one already exists.
        \item Let's say that you see several tickets that come up. First, check the ticket
        status.
        \begin{itemize}
            \item If all tickets are "Resolved", then you are fine to re-open one.
            You will always re-open the most recent, or most-related ticket.
            \item If there is an OPEN ticket related to the issue, then someone is
            already working on this issue and you can not continue creating a ticket.
            \item If there are NO TICKETS matching, then you can create a new ticket.
        \end{itemize}
        \item If you want to re-open a closed ticket, first you will have to assign
        the ticket to yourself. Under the "People" Tab, choose your name from the
        "Owner" drop-down, and hit "Save Changes".
        \item Then to re-open the ticket, hit "Re-Open" under the "Actions" tab.
        \begin{itemize}
            \item You may now work on the ticket like you would any other.
        \end{itemize}
        \item If there are no tickets matching, you will need to create a new ticket.
        \begin{itemize}
            \item At the top-right of the page next to the search bar is a ticket creation
            button. From the drop-down, select "htcondor-inf" - This will open the page
            to create a new ticket in the htcondor-inf queue.
            \item In the right-most box labeled "Basics", put yourself in the "Owner"
            field and "CHTC" in the inf\_subgroup field.
            \item In the left-most box, enter an appropriate subject ("e1000 down"),
            and a short-description if desired.
            \item Click "Create" on the bottom of the page.
            \item Assuming you made yourself the ticket owner, you will now see this ticket
            in your queue!
        \end{itemize}
        \item LASTLY, if you re-opened or created a new ticket, you need to acknowledge
        that you did so on Icinga so that other poeple won't create a duplicate ticket.
        \begin{itemize}
            \item Return to Icinga, and on the dashboard for that particular node, click
            on "Acknowledge" under the "Problem Handling" section.
            \item enter a short message, (eg "Created a ticket - [your name]").
            \item Hit "Acknowledge Problem" - And you're done!
        \end{itemize}
    \end{enumerate}

    Congratulations - you now know how to find problems on Icinga and create a ticket
    in order to fix it!
\clearpage

\section{Checking for Errors}
    \subsection{Monitoring with Icinga}
        \subsubsection{Icinga Basics}
        \subsubsection{Web Interface}
        \subsubsection{Icinga CLI}
    \subsection{Error Logs}
    \subsection{Hardware Errors}
\clearpage

\section{Advanced Troubleshooting}
    TODO
\clearpage

\section{Advanced Topics}
    \subsection{Networking}
        \subsubsection{Networking Basics}
        \subsubsection{CHTC Network Structure}
        \subsubsection{Troubleshooting Networking Issues}
    \subsection{Making Your Life Easier}
    \begin{enumerate}
        \item Rebooting stubborn nodes remotely
            \begin{itemize}
                \item There's a handy "magic key" called sysrq that is managed through the /proc filesystem in Linux. Quite a few things can be done with this, but a faithful adminstrative trick is to echo a 'key' to the sysrq-trigger to force a reboot when performing a {\fontfamily{cmtt}\selectfont \$ sudo reboot } just doesn't cut it.
                \item First, you'll need to su into root: {\fontfamily{cmtt}\selectfont \$ sudo su - }
                \item Next, {\fontfamily{cmtt}\selectfont \$ echo "1" > /proc/sys/kernel/sysrq } to enable the sysrq 'key'.
                 \item Lastly, in order to force the node to reboot, {\fontfamily{cmtt}\selectfont \$ echo "b" > /proc/sysrq-trigger }
                \item Not as good as full IPMI control but useful for pesky nodes. We'll go over IPMI next.
             \end{itemize}
    \end{enumerate}


\clearpage


% APPENDIX
\appendix
\section{Node Locations}
    \subsection{B240}
        \begin{center}
        \begin{tabular}{ |c|c|c|c|c|c|c|c|c| }
        \hline
        Rack & A2 & A4 & C1 & C2 & C4 & E2 & E5 & E6 \\
        \hline
        \multirow{1}{3em}{Node}

        &      & mussel  & e036    & c031 & atlas13    & e061 & atlas80 & atlas64 \\
        &      & atlas18 & e027    & c032 & atlas14    & e060 & atlas81 & atlas65 \\
        &      & atlas19 & e039    & c033 & atlas28    & e059 & atlas82 & atlas66 \\
        &      & atlas20 & atlas17 & c035 & atlas15    & e058 & atlas83 & atlas67 \\
        &      & e047    & atlas11 & c036 & starfish   & e002 & atlas84 & atlas68 \\
        &      & e035    & atlas12 & c037 & e013       & e025 & atlas85 & atlas69 \\
        &      & e034    & atlas16 & c038 & e012       & e030 & atlas86 & atlas70 \\
        &      & [???]   &         & c039 & e011       & e057 & atlas87 & atlas71 \\
        &      & e006    &         & c040 & spalding11 & e022 & atlas88 & atlas72 \\
        &      & cobbler &         & c041 & spalding10 & e040 & atlas89 & atlas73 \\
        &      & e010    &         & c020 & spalding09 & e023 & atlas90 & atlas74 \\
        &      & e045(missing)   &         & c021 & spalding08 & e018 & atlas91 & atlas75 \\
        &      & e044    &         & c022 & spalding07 & e016 & atlas92 & atlas76 \\
        &      & [???]   &         & c023 & spalding06 & e026 & atlas93 & atlas77 \\
        &      & e003    &         & c025 & spalding05 & e028 & atlas95 & atlas78 \\
        &      &         &         & c027 & c081       & e041 & atlas96 & atlas79 \\
        &      &         &         & c028 & c082       & e038 & atlas97 & atlas08 \\
        &      &         &         & c029 & c084       & e042 & atlas98 & atlas42 \\
        &      &         &         & c030 & c085       & e046 & atlas99 & atlas62 \\
        & e049 &         &         & c046 & c086       & e056 &         &         \\
        & e050 &         &         & c047 & c088       & e052 &         &         \\
        & e051 &         &         & c058 & c089       & e043 &         &         \\
        & e054 &         &         & c059 & c090       & db1* &         &         \\
        & e055 &         &         & c060 & c077       & e460 &         &         \\
        & e062 &         &         & c061 & c078       & e461 &         &         \\
        & e063 &         &         & c062 &            & e462 &         &         \\
        & e064 &         &         & c064 &            & e463 &         &         \\
        & e065 &         &         & c065 &            & e464 &         &         \\
        & e031 &         &         & c069 &            & e465 &         &         \\
        &      &         &         & c002 &            &      &         &         \\
        &      &         &         & c004 &            &      &         &         \\
        &      &         &         & c007 &            &      &         &         \\
        &      &         &         & c008 &            &      &         &         \\
        &      &         &         & c012 &            &      &         &         \\
        &      &         &         & c015 &            &      &         &         \\
        &      &         &         & c016 &            &      &         &         \\
        &	   &	     &         & c017 &            &	  &		    &		  \\
        &	   &	     &         & c070 &            &	  &		    &		  \\
        &	   &	     &         & c071 &            &	  &		    &		  \\
        &	   &	     &         & c074 &            &	  &		    &		  \\


        \hline
        \end{tabular}
        \end{center}

        \begin{center}
        \begin{tabular}{ |c|c|c|c|c| }
        \hline
        Rack & G1 & G2 & G5 & G6 \\
        \hline
        \multirow{1}{3em}{Node}

        & satellite & e024 & [???]   & atlas44 \\
        & e029    & e053   & atlas29 & atlas45 \\
        & stress1 & e009   & atlas30 & atlas46 \\
        & stress2 & e008   & atlas31 & atlas47 \\
        & stress3 & e007   & atlas32 & atlas48 \\
        & stress4 & e005   & atlas33 & atlas49 \\
        & host-5  & e089   & atlas34 & atlas50 \\
        &         & e090   & atlas35 & atlas51 \\
        &         & e088*  & atlas36 & atlas52 \\
        &         & e087   & atlas37 & atlas53 \\
        &         & e086   & atlas38 & atlas54 \\
        &         & e085   & atlas39 & atlas55 \\
        &         & e084   & atlas40 & atlas56 \\
        &         & e083   & atlas41 & atlas57 \\
        &         & e082   & atlas43 & atlas58 \\
        &         & e081   & atlas03 & atlas59 \\
        &         & e080   & atlas04 & atlas60 \\
        &         & e079   & atlas05 & atlas61 \\
        &         & e078   & atlas06 & atlas63 \\
        &         & e077 &&\\
        &         & e076 &&\\
        &         & e075 &&\\
        &         & e074 &&\\
        &         & e073 &&\\
        &         & e072 &&\\
        &         & e071 &&\\
        &         & e070 &&\\
        &         & e069 &&\\
        &         & e068 &&\\
        &         & e067 &&\\

        \hline
        \end{tabular}
        \end{center}

    \subsection{2360/CSL}
        \begin{center}
        \begin{tabular}{ |c|c|c|c|c|c|c| }
        \hline
        Rack & GR 6 & GR 0 & GR 4 & GR 3 & 10 & GR 7 \\
        \hline
        \multirow{1}{3em}{Node}

        & atlas07 & e299 & e339 & e379 & e413 & e418 \\
        & atlas02 & e298 & e338 & e378 & e412 & e417 \\
        & mem3    & e297 & e337 & e377 & e411 & e416 \\
        & mem2    & e296 & e336 & e376 & e410 & e415 \\
        & mem1    & e295 & e335 & e375 & e409 & e414 \\
        & gpu4    & e294 & e334 & e374 & e408 & e454 \\
        & host-22 & e293 & e333 & e373 & e407 & e453 \\
        & host-20 & e292 & e332 & e372 & e406 & e452 \\
        & host-18 & e291 & e331 & e371 & e405 & e451 \\
        & host-16 & e290 & e330 & e370 & e404 & e450 \\
        & host-14 & e289 & e329 & e369 & e403 & e449 \\
        & host-12 & e288 & e328 & e368 & e402 & e448 \\
        & host-10 & e287 & e327 & e367 & e401 & e447 \\
        &         & e286 & e326 & e366 & e400 & e446 \\
        &         & e285 & e325 & e365 & e399 & e445 \\
        &         & e284 & e324 & e364 & e398 & e444 \\
        &         & e283 & e323 & e363 & e397 & e443 \\
        &         & e282 & e322 & e362 & e396 & e442 \\
        &         & e281 & e321 & e361 & e395 & e441 \\
        &         & e280 & e320 & e360 & e394 & e440 \\
        &         & e279 & e319 & e359 & e393 & e439 \\
        &         & e278 & e318 & e358 & e392 & e438 \\
        &         & e277 & e317 & e357 & e391 & e437 \\
        &         & e276 & e316 & e356 & e390 & e436 \\
        &         & e275 & e315 & e355 & e389 & e435 \\
        &         & e274 & e314 & e354 & e388 & e434 \\
        &         & e273 & e313 & e353 & e387 & e433 \\
        &         & e272 & e312 & e352 & e386 & e432 \\
        &         & e271 & e311 & e351 & e385 & e431 \\
        &         & e270 & e310 & e350 & e384 & e430 \\
        &         & e269 & e309 & e349 & e383 & e429 \\
        &         & e268 & e308 & e348 & e382 & e428 \\
        &         & e267 & e307 & e347 & e381 & e427 \\
        &         & e266 & e306 & e346 & e380 & e426 \\
        &         & e265 & e305 & e345 &      & e425 \\
        &         & e264 & e304 & e344 &      & e424 \\
        &         & e263 & e303 & e343 &      & e423 \\
        &         & e262 & e302 & e342 &      & e422 \\
        &         & e261 & e301 & e341 &      & e421 \\
        &         & e260 & e300 & e340 &      & e420 \\
        &		  &      &      &      &      & e419  \\

        \hline
        \end{tabular}
        \end{center}

    \clearpage

    \subsection{3370}
        \begin{center}
        \begin{tabular}{ |c|c|c|c|c|c|c|c|c| }
        \hline
        Rack & 1 & 4 & 5 & 6 & 7 & 8 & 9 & GR 5 \\
        \hline
        \multirow{1}{3em}{Node}

        & e198 & swamp-nas & osghost        & host-6     & e222    & submit-4 & e116           & spalding-4 \\
        & e197 & swamp05 & itb-data1        & pagesubmit & e220    & host-23  & e117           & spalding-1 \\
        & e196 & swamp04 & itb-data2        & atlas21    & e219    & host-21  & nmi-0067       & spalding-2 \\
        & e195 & swamp03 & itb-data3        & atlas22    & e215    & host-19  & e115           & spalding-3 \\
        & e194 & swamp02 & itb-data4        & atlas27    & e214    & host-17  & gpu-1          &            \\
        & e193 & swamp01 & itb-data5        & atlas26    & e119    & host-15  & e114           &            \\
        & e192 &         & itb-data6        & atlas25    & e212    & host-13  & atlas10        &            \\
        & e191 &         & itb-host1        & atlas24    & e211    & host-11  & atlas09        &            \\
        & e190 &         & itb-host2        & atlas23    & e210    & e238     & e111           &            \\
        & e189 &         & itb-host3        &            & e209    & e237     & matlab-build-5 &            \\
        & e188 &         & vdt-bastion      &            & e208    & e236     & e113           &            \\
        & e187 &         & vdt-centos5-test &            & e207    & e235     & e112           &            \\
        & e186 &         & vdt-debian6-test &            & e206    & e234     & e246           &            \\
        & e185 &         & vdt-debian7-test &            & e205    & e233     & e245           &            \\
        & e184 &         &                  &            & e204    & e232     & e244           &            \\
        & e183 &         &                  &            & e203    & e231     & e243           &            \\
        & e182 &         &                  &            & e202    & e230     & e242           &            \\
        & e181 &         &                  &            & e201    & e229     & e241           &            \\
        & e180 &         &                  &            & e200    & e228     & e240           &            \\
        & e179 &         &                  &            & e199    & e227     & e239           &            \\
        & e178 &         &                  &            & host-24 & e226     & e259           &            \\
        & e177 &         &                  &            &         & e225     & e258           &            \\
        & e176 &         &                  &            &         & e224     & e256           &            \\
        & e175 &         &                  &            &         & e223     & e255           &            \\
        & e174 &         &                  &            &         &          & e254           &            \\
        & e173 &         &                  &            &         &          & e253           &            \\
        & e172 &         &                  &            &         &          & e252           &            \\
        & e171 &         &                  &            &         &          & e251           &            \\
        & e170 &         &                  &            &         &          & e250           &            \\
        & e169 &         &                  &            &         &          & e249           &            \\
        & e168 &         &                  &            &         &          & e248           &            \\
        & e167 &         &                  &            &         &          & e247           &            \\
        & e166* &         &                  &            &         &          &                &            \\
        & e165 &         &                  &            &         &          &                &            \\
        & e164* &         &                  &            &         &          &                &            \\
        & e163 &         &                  &            &         &          &                &            \\
        & e162 &         &                  &            &         &          &                &            \\
        & e161 &         &                  &            &         &          &                &            \\
        & e160 &         &                  &            &         &          &                &            \\
        & e159 &         &                  &            &         &          &                &            \\
        & e158 &         &                  &            &         &          &                &            \\
        & e157 &         &                  &            &         &          &                &            \\
        & e156 &         &                  &            &         &          &                &            \\
        & e155 &         &                  &            &         &          &                &            \\
        & e154 &         &                  &            &         &          &                &            \\
        & e153 &         &                  &            &         &          &                &            \\
        & e152 &         &                  &            &         &          &                &            \\
        & e151 &         &                  &            &         &          &                &            \\
        \hline
        \end{tabular}
        \end{center}

    \clearpage

    \subsection{WID Data Center}
        \begin{center}
        \begin{tabular}{ |c|c|c|c|c|}
        \hline
        Rack & A14 & A12 & B1 & B5 \\
        \hline
        \multirow{1}{3em}{Node}

        &       & deepdivesubmit & wid-003        & e110 \\
        & e095  & host-3         & [???]          & e109 \\
        & e457  & [???]          & e019(swamp)    & e108 \\
        & e121  & [???]          & e017           & e107 \\
        & e122  & [???]          & e020           & e106 \\
        & e123  & host-7         & e033           & e105 \\
        & e124  & submit-5       & e021           & e104 \\
        & e125  & submit-3       & e014           & e103 \\
        & e126  & quickstep      & e015           & e102 \\
        & e127  & wid-service-1  & matlab-build-1 & e101 \\
        & e128  & e092(missing)  & e001           & e100 \\
        & e129  & osg-ss-se      & e091(swamp)    & e099 \\
        & e130  & [batlab]       & [???]          & e098 \\
        & e131  & host-1         & [???]          & e097 \\
        & e132  & hypervisor0    & [???]          & e096 \\
        & e133  &                & e458           &      \\
        & e134  &                & e459           &      \\
        & e135  &                & e466           &      \\
        & e136  &                & e467           &      \\
        & e137  &                & e468           &      \\
        & e138  &                &                &      \\
        & e139  &                &                &      \\
        & e140  &                &                &      \\
        & e141  &                &                &      \\
        & e142  &                &                &      \\
        & e143  &                &                &      \\
        & e144  &                &                &      \\
        & e145  &                &                &      \\
        & e146  &                &                &      \\
        & e147  &                &                &      \\
        & e148  &                &                &      \\
        & e149  &                &                &      \\
        & e150* &                &                &      \\

        \hline
        \end{tabular}
        \end{center}

        \begin{center}
        \begin{tabular}{ |c|c|c|c|c|c|c|c|c|c|c|}
        \hline
        Rack & Z1-R11 & Z1-R10 & Z1-R8 & Z1-R7 & Z1-R5 & Z2-R11 & Z2-R10 & Z2-R8 & Z2-R7 & Z2-R5 \\
        \hline
        \multirow{1}{3em}{Node}
        & aci-336 & aci-288 & aci-storage-7  & aci-service-1 & aci-144 & aci-096 & aci-048 & aci-192 & aci-240 & aci-344 \\
        & aci-335 & aci-287 & aci-storage-8  & aci-service-2 & aci-143 & aci-095 & aci-047 & aci-191 & aci-239 & aci-343 \\
        & aci-334 & aci-286 & aci-storage-9  & aci-service-3 & aci-142 & aci-094 & aci-046 & aci-190 & aci-238 & aci-342 \\
        & aci-333 & aci-285 & aci-storage-10 & aci-storage-1 & aci-141 & aci-093 & aci-045 & aci-189 & aci-237 & aci-341 \\
        & aci-332 & aci-284 & aci-storage-11 & aci-storage-2 & aci-140 & aci-092 & aci-044 & aci-188 & aci-236 & aci-340 \\
        & aci-331 & aci-283 & aci-storage-12 & aci-storage-3 & aci-139 & aci-091 & aci-043 & aci-187 & aci-235 & aci-339 \\
        & aci-330 & aci-282 & aci-storage-13 & aci-storage-4 & aci-138 & aci-090 & aci-042 & aci-186 & aci-234 & aci-338 \\
        & aci-329 & aci-281 & aci-storage-14 & aci-storage-5 & aci-137 & aci-089 & aci-041 & aci-185 & aci-233 & aci-337 \\
        & aci-328 & aci-280 & aci-storage-15 & aci-storage-6 & aci-136 & aci-088 & aci-040 & aci-184 & aci-232 &         \\
        & aci-327 & aci-279 & aci-storage-16 &               & aci-135 & aci-087 & aci-039 & aci-183 & aci-231 &         \\
        & aci-326 & aci-278 &                &               & aci-134 & aci-086 & aci-038 & aci-182 & aci-230 &         \\
        & aci-325 & aci-277 &                &               & aci-133 & aci-085 & aci-037 & aci-181 & aci-229 &         \\
        & aci-324 & aci-276 &                &               & aci-132 & aci-084 & aci-036 & aci-180 & aci-228 &         \\
        & aci-323 & aci-275 &                &               & aci-131 & aci-083 & aci-035 & aci-179 & aci-227 &         \\
        & aci-322 & aci-274 &                &               & aci-130 & aci-082 & aci-034 & aci-178 & aci-226 &         \\
        & aci-321 & aci-273 &                &               & aci-129 & aci-081 & aci-033 & aci-177 & aci-225 &         \\
        & aci-320 & aci-272 &                &               & aci-128 & aci-080 & aci-032 & aci-176 & aci-224 &         \\
        & aci-319 & aci-271 &                &               & aci-127 & aci-079 & aci-031 & aci-175 & aci-223 &         \\
        & aci-318 & aci-270 &                &               & aci-126 & aci-078 & aci-030 & aci-174 & aci-222 &         \\
        & aci-317 & aci-269 &                &               & aci-125 & aci-077 & aci-029 & aci-173 & aci-221 &         \\
        & aci-316 & aci-268 &                &               & aci-124 & aci-076 & aci-028 & aci-172 & aci-220 &         \\
        & aci-315 & aci-267 &                &               & aci-123 & aci-075 & aci-027 & aci-171 & aci-219 &         \\
        & aci-314 & aci-266 &                &               & aci-122 & aci-074 & aci-026 & aci-170 & aci-218 &         \\
        & aci-313 & aci-265 &                &               & aci-121 & aci-073 & aci-025 & aci-169 & aci-217 &         \\
        & aci-312 & aci-264 &                &               & aci-120 & aci-072 & aci-024 & aci-168 & aci-216 &         \\
        & aci-311 & aci-263 &                &               & aci-119 & aci-071 & aci-023 & aci-167 & aci-215 &         \\
        & aci-310 & aci-262 &                &               & aci-118 & aci-070 & aci-022 & aci-166 & aci-214 &         \\
        & aci-309 & aci-261 &                &               & aci-117 & aci-069 & aci-021 & aci-165 & aci-213 &         \\
        & aci-308 & aci-260 &                &               & aci-116 & aci-068 & aci-020 & aci-164 & aci-212 &         \\
        & aci-307 & aci-259 &                &               & aci-115 & aci-067 & aci-019 & aci-163 & aci-211 &         \\
        & aci-306 & aci-258 &                &               & aci-114 & aci-066 & aci-018 & aci-162 & aci-210 &         \\
        & aci-305 & aci-257 &                &               & aci-113 & aci-065 & aci-017 & aci-161 & aci-209 &         \\
        & aci-304 & aci-256 &                &               & aci-112 & aci-064 & aci-016 & aci-160 & aci-208 &         \\
        & aci-303 & aci-255 &                &               & aci-111 & aci-063 & aci-015 & aci-159 & aci-207 &         \\
        & aci-302 & aci-254 &                &               & aci-110 & aci-062 & aci-014 & aci-158 & aci-206 &         \\
        & aci-301 & aci-253 &                &               & aci-109 & aci-061 & aci-013 & aci-157 & aci-205 &         \\
        & aci-300 & aci-252 &                &               & aci-108 & aci-060 & aci-012 & aci-156 & aci-204 &         \\
        & aci-299 & aci-251 &                &               & aci-107 & aci-059 & aci-011 & aci-155 & aci-203 &         \\
        & aci-298 & aci-250 &                &               & aci-106 & aci-058 & aci-010 & aci-154 & aci-202 &         \\
        & aci-297 & aci-249 &                &               & aci-105 & aci-057 & aci-009 & aci-153 & aci-201 &         \\
        & aci-296 & aci-248 &                &               & aci-104 & aci-056 & aci-008 & aci-152 & aci-200 &         \\
        & aci-295 & aci-247 &                &               & aci-103 & aci-055 & aci-007 & aci-151 & aci-199 &         \\
        & aci-294 & aci-246 &                &               & aci-102 & aci-054 & aci-006 & aci-150 & aci-198 &         \\
        & aci-293 & aci-245 &                &               & aci-101 & aci-053 & aci-005 & aci-149 & aci-197 &         \\
        & aci-292 & aci-244 &                &               & aci-100 & aci-052 & aci-004 & aci-148 & aci-196 &         \\
        & aci-291 & aci-243 &                &               & aci-099 & aci-051 & aci-003 & aci-147 & aci-195 &         \\
        & aci-290 & aci-242 &                &               & aci-098 & aci-050 & aci-002 & aci-146 & aci-194 &         \\
        & aci-289 & aci-241 &                &               & aci-097 & aci-049 & aci-001 & aci-145 & aci-193 &         \\

        \hline
        \end{tabular}
        \end{center}



\clearpage

\section{List of Resources}
    TODO - A useful list of external resources.
    \begin{itemize}
        \item http://pages.cs.wisc.edu/~van-lyse/ - Neil's CS Page contains tons
        of useful CHTC links.
        \item monitor0.chtc.wisc.edu - Our webpage for server monitoring. Contains
        links to Icinga, Grafana, Ganglia, and more.
        \item https://chtc-sa.cs.wisc.edu/trac/priv - CHTC Private Wiki. Login required,
        contains a massive amount of information and guides. Some things are dated, but
        still extremely useful.
    \end{itemize}
\clearpage

\section{Glossary}
    TODO - Glossary of terms commonly used in this manual and in daily work.
    \begin{itemize}
        \item Cobbler - Cobbler is a frontend tool for configuring Linux network
        installs with PXE boot. Learn more: http://cobbler.github.io/
        \item Icinga - An open-source system monitoring tool with a web interface.
        Our Icinga server is at monitor0.chtc.wisc.edu. Learn more at: https://www.icinga.org/
        \item Puppet - Puppet is a tool for managing automatic configuration of
        systems. Our puppetmaster machine is wid-service-1. Learn more:
        https://puppet.com/
        \item RT (Request Tracker) - Ticket-tracking software. Access RT at:
        https://crt.cs.wisc.edu/rt/
    \end{itemize}
\clearpage

\end{document}

